---
title: "Exploratory Data Analysis on the Air Quality Dataset"
output:
  html_document:
    df_print: paged
---

### Load Packages
First things first, load the packages needed for further analysis.
```{r echo=TRUE,results='hide'}
library(dplyr) # tools for data manipulation
library(tibble) # tools for better data formatting than the traditional data frame
library(dlookr) # tools for data exploration
library(htmltools) # tools for HTML generation and output
```

### Load Dataset
The dataset used is `airquality` which is already available in R, the `airquality` dataset is daily air quality measurements in New York, May to September 1973.
```{r}
# view data
head(airquality)
```

### Data Diagnosis

#### *General Data Diagnosis*
The diagnosis of all variables in the `airquality` dataset.
```{r}
diagnose(airquality)
```
* `variables` : Variable Names
* `types` : Data Type of the Variables
* `missing_count` : Number of Missing Values
* `missing_percent` : Percentage of Missing Values
* `unique_count` : Number of Unique Values
* `unique_rate` : Rate of Unique Value, Unique Count/Number of Observation

#### *Categorical Data Diagnosis*
The diagnosis of categorical variables in the `airquality` dataset.
```{r}
diagnose_category(airquality)
```
The result is NULL because there's no categorical variable in the `airquality` dataset.

#### *Numerical Data Diagnosis*
The diagnosis of numerical variables in the `airquality` dataset.
```{r}
diagnose_numeric(airquality)
```
* `min` : Minimum Value
* `Q1` : 1/4 Quartile, 25th Percentile
* `mean` : Arithmetic Mean
* `median` : Median, 50th Percentile
* `Q3` : 3/4 Quartile, 75th Percentile
* `max` : Maximum Value
* `zero` : Number of Observations with a Value of 0
* `minus` : Number of Observations with Negative Numbers
* `outlier` : Number of Outliers

#### *Outlier Diagnosis*
```{r}
diagnose_outlier(airquality)
```

#### *Outlier Plot*
```{r}
airquality %>%
  plot_outlier(Ozone, Wind)
```

#### *Missing Value Intersection Plot*
```{r}
plot_na_intersect(airquality)
```

### Data Diagnosis Made Easier!
The simple and fast way to perform data exploration, using `diagnose_web_report` from `dlookr` package.
```{r warning=FALSE,message=FALSE,results='hide'}
diagnose_web_report(airquality,output_file="airquality_Diagnosis_Report.html",output_dir="~/Downloads/")
```

```{r, echo=FALSE}
htmltools::knit_print.html("airquality_Diagnosis_Report.html")
```

### Descriptive Statistics
The deep dive into the `airquality` dataset's statistics.

#### Summary
```{r}
summary(airquality)
```

#### Description
```{r}
describe(airquality)
```

#### Normality Checking
```{r}
normality(airquality)
```

#### Normality Plot
```{r}
airquality %>%
  plot_normality(Ozone, Wind)
```

#### Correlation Matrix
```{r}
correlate(airquality)
```

#### Correlation Plot
```{r}
plot_correlate(airquality)
```


### Data Exploration Made Easier!
The simple and fast way to perform data exploration, using `eda_web_report` from `dlookr` package.
```{r warning=FALSE,message=FALSE,results='hide'}
eda_web_report(airquality,output_file="airquality_Exploration_Report.html",output_dir="~/Downloads/")
```

```{r, echo=FALSE}
htmltools::knit_print.html("airquality_Exploration_Report.html")
```

### Data Transformation
The data transformation is used according to the needs.

#### Handling Missing Values
Missing values can be handeled by two methods:

##### Remove Missing Values
```{r}
NROW(airquality$Ozone)
```
```{r}
x <- na.omit(airquality$Ozone)
NROW(x)
```

##### Impute Missing Values
Methods:

* `mean` : Arithmetic Mean
* `median` : Median
* `mode` : Mode
* `knn` : K-nearest Neighbors (target variable must be specified)
* `rpart` : Recursive Partitioning and Regression Trees (target variable must be specified)
* `mice` : Multivariate Imputation by Chained Equations (target variable must be specified, random seed must be set)

```{r}
ozone_impute <- imputate_na(airquality, Ozone, method = "mean")
summary(ozone_impute)
```
```{r}
plot(ozone_impute)
```

#### Handling Outliers
Outliers can be handeled by two methods:

##### Remove Outliers
```{r}
Q1 <- quantile(airquality$Wind, .25)
Q3 <- quantile(airquality$Wind, .75)
IQR <- IQR(airquality$Wind)
no_outliers <- subset(airquality, airquality$Wind > (Q1 - 1.5*IQR) & airquality$Wind < (Q3 + 1.5*IQR))
NROW(no_outliers)
```

##### Impute Outliers
Methods:

* `mean` : Arithmetic Mean
* `median` : Median
* `mode` : Mode
* `capping` : Impute the Upper Outliers with 95th Percentile and Impute the Bottom Outliers with 5th Percentile

```{r}
out_wind <- imputate_outlier(airquality, Wind, method = "capping")
summary(out_wind)
```
```{r}
plot(out_wind)
```

#### Standardization
Methods:

* `zscore` : Z-score Transformation, (x - mu) / sigma
* `minmax` : MinMax Transformation, (x - min) / (max - min)

```{r}
air_trans<- transform(airquality$Wind, method = "minmax")
boxplot(air_trans)
```

#### Resolving Skewness
Methods:

* `log` : Log Transformation, log(x)
* `log+1` : Tog Transformation, log(x + 1), used for values that contain 0
* `sqrt` : Square Root Transformation
* `1/x` : 1 / x Transformation
* `x^2` : X^2 Transformation
* `x^3` : X^3 Transformation

```{r}
Ozone_log = transform(airquality$Ozone, method = "log")
summary(Ozone_log)
```
```{r}
plot(Ozone_log)
```